\papertitle

### 2014-03-17 final-report/paper.tex
Skew and no skew figures.

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}

\usepackage{graphicx}

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context} that possible to implement conveniently using D3.

@@

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{images/skew}
    \caption{Data skew.}
    \label{fig:skew}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{images/no-skew}
    \caption{No data skew.}
    \label{fig:no-skew}
  \end{subfigure}
  \caption{The network view shows a distinctive pattern when there is data skew. Figure~\ref{fig:skew} shows that most tuples are sent to worker 1 and 5 (origin: x-axis, destination: y-axis).}
  \label{fig:network}
\end{figure}
